---
title: "Sri Lanka"
toc: true
format:
  html:
    theme: default
---

<!-- Google tag (gtag.js) -->
<script async src="https://www.googletagmanager.com/gtag/js?id=G-MMF7S9CQZW"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'G-MMF7S9CQZW');
</script>

# District-wise weekly Dengue cases from 2006 to 2023-present

```{r, echo=TRUE, eval=TRUE}
library(denguedatahub)
library(tsibble)
srilanka_weekly_data

```

## Visualize `srilanka_weekly_data`

```{r}
visdat::vis_dat(srilanka_weekly_data)
```

## Time series visualization 

```{r, warning=FALSE, message=FALSE, fig.height=20, fig.width=15}
library(plotly)
library(viridis)

#  Visualizing colombo district cases
number_ticks <- function(n) {function(limits) pretty(limits, n)}
srilanka_weekly_data %>%  
ggplot(aes(x=start.date, y=cases)) + geom_line()  + 
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(vars(district), scales = "free_y", ncol=5)


```

# Function to extract dengue cases from weekly epidemiological reports published by [Epidemiology Unit, Ministry of Health Sri Lanka](https://www.epid.gov.lk/web/index.php?option=com_content&view=article&id=148&Itemid=449&lang=en)

## Step 1: Get PDF links corresponds to 2024

```{r}
library(denguedatahub)
link2024 <- get_pdflinks_srilanka(url="https://www.epid.gov.lk/weekly-epidemiological-report/weekly-epidemiological-report", volume.number="Vol_51")
head(link2024)
```

## Step 2: Convert PDF file data into tibble format

This example illustrates the content of the first 2 pages of the PDF.

```{r}
link2024[[1]][1] ## No 1 WER
link2024[[2]][1] ## No 30 WER
data2024 <- convert_slwer_to_tidy(year=2024, 
                                         reports.url=link2024[1:2], 
                                         start.date.first = "2023-12-23",
                                         end.date.first = "2023-12-29",
                                         start.date.last = "2023-12-30", 
                                         end.date.last = "2024-1-05",
                                         week.no=c(52, 1))
head(data2024)
```

## Function to download Weekly Epidemiological Reports (WEK) and save them inside the local directory

```r
download_pdfwer_srilanka(url="https://www.epid.gov.lk/weekly-epidemiological-report/weekly-epidemiological-report", folder.name="dengue", volume.number="Vol_51")
```