---
title: "USA"
toc: true
format:
  html:
    theme: default
---

<!-- Google tag (gtag.js) -->
<script async src="https://www.googletagmanager.com/gtag/js?id=G-MMF7S9CQZW"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag('js', new Date());

  gtag('config', 'G-MMF7S9CQZW');
</script>



```{r, warning=FALSE, message=FALSE}
library(denguedatahub)
library(tsibble)
```

## Dengue and severe dengue cases and deaths for subregions of the Americas

```{r}
head(americas_annual_data)
```

## All dengue cases by week in US states and territories, 2010 - 2023

```{r}
head(cdc_casesby_week)
```

## Dengue cases by age group and sex in US states and territories, 2010 - 2023


```{r}
head(cdc_dengue_agesex)
```

## All dengue cases by jurisdiction of residence in US states and territories, 2010 - 2023


```{r}
head(cdc_dengue_casesbyjurisdiction)
```

## All dengue cases by county of residence in US states and territories, 2010 - 2023


```{r}
head(cdc_dengue_countyyear)
```

## Locally acquired dengue cases by year, 2010 - 2023


```{r}
head(cdc_local_dengue_cases)
```

## Travel associated dengue cases by year, 2010 - 2023


```{r}
head(cdc_travel_associated_dengue_cases)
```


##  Annual number of dengue fever infections in the USA


```{r}
head(cdc_usa_dengue_infection)
```

Data Source: [Centers for Disease Control and Prevention](https://www.cdc.gov/index.html)